Agile Inter-team Software Development

### 2019-01-20 Draft/Parts/Conclusion.tex
Changed files to use one line per sentence (better change tracking).
Adding transition paragraph for process/tech/arch.

\section{Conclusion} 
\label{sec:conclusion}
As we have seen, the issue of inter-team communication can be a big problem in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked. To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture / design which is available to all the teams and thus provides a common vision to all the teams involved.

>>>>

\section{Conclusion} 
\label{sec:conclusion}
As we have seen, inter-team communication can be an obstacle in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked.
To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture and design which is available to all the teams and thus provides a common framework to all the teams involved.

### 2019-01-20 Draft/Parts/Main.tex
Adding transition paragraph for process/tech/arch.

\section{NAME ME}

>>>>

\section{NAME ME} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at different levels need to have ways to pass information.
This can be addressed by adaptions in development process and leveraging technology.
Second, the quality of communication needs to be accurate.
This can be addressed by sound system specification through architecture and design.
